%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingGTECH}[7]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
      {\small #7 \vspace{-2pt}}
    \end{tabular*}\vspace{-5pt}
}

%\newcommand{\resumeSubheadingNEU}[5]{
%    \begin{tabular}{{0.7\textwidth}{0.3\textwidth}}
%      \textbf{#1} & #2 \\
%      \textit{\small#3} & \textit{\small #4} \\
%      {\small#5} & {\small#5} \\
%    \end{tabular}
%}

\newcommand{\resumeSubheadingNEU}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      {\small#5}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumePub}[1]{
  \item\small{
    #1
  }
}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Brian Crafton}} & Email : \href{mailto:brian.crafton@gatech.edu}{brian.crafton@gatech.edu} \\
  Mobile : +1-774-571-1340 & Github: bcrafton \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheadingGTECH
      {Georgia Institute of Technology}{Atlanta, GA}
      {Ph,D. Computer Engineering}{May 2022 }
      {MS. Computer Engineering}{May 2019 }
      {Advanced Computer Architecture, CAD - Synthesis, CAD - PD, VLSI, Neuromorhpic Computing }

    \resumeSubheadingNEU
      {Northeastern University}{Boston, MA}
      {Bachelor of Science in Computer Engineering;  GPA: 3.7}{Aug 2013 - May 2017}
      {Compilers, Operating Systems, Nanofab, VLSI, Parallel Programming, Algorithms 1, 2, \& 3}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ICSRL, Georgia Institute of Technology}{Atlanta, GA}
      {Research Assistant}{May 2018 -}
      \resumeItemListStart
        \resumeItem{Emerging Device Circuits}
          { Worked with device collaborators to create circuit simulations using FeFETs and memristors  }
        \resumeItem{Spiking Networks}
          { Developed models from experimental data for ferroelectric neurons and synapses implementing STDP to solve learning problems }
        \resumeItem{Memristive Neural Network}
          { Designed memristive neural network to solve MNIST }
        \resumeItem{Local Learning}
          { Using variation of feedback alignment algorithm to allow deep networks to learn locally }
      \resumeItemListEnd

    \resumeSubheading
      {GTCAD, Georgia Institute of Technology}{Atlanta, GA}
      {Research Assistant}{Aug 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Compiler}
          { Developed frontend for modeling protocols. Syntax eventually translated to an abstract syntax tree and finally turned into a finite state machine }
        \resumeItem{Algorithms}
          { Implemented merging algorithms to combine two protocols to automatically generate a finite state machine for a hardware translator }
        \resumeItem{Full Flow}
          { Implemented a full flow to translate the high level syntax into Verilog and finally go down to netlist and layout }
      \resumeItemListEnd

    \resumeSubheading
      {AMD}{Boxborough MA}
      {Engineer Coop}{May-Aug 2017, July-Dec 2016}
      \resumeItemListStart
        \resumeItem{Performance Verification}
          {Lead performance verification. Debugged bottlenecks and proposed solutions }
        \resumeItem{Cache}
          {Debugged cache bottleneck and offered tradeoffs of different models (size and eviction policy) }
        \resumeItem{Functional Verification}
          {Implemented tests at block level. Set register values and drive random and constant stimulus. Debugged RTL failures and proposed solutions }
        \resumeItem{Subblock Testbench}
          {Implemented and owned subblock test bench. Stressed cache and compression blocks }
        \resumeItem{Tools}
          {Implemented Python tools to automate verification techniques }

      \resumeItemListEnd

    \resumeSubheading
      {Northeastern University}{Boston, MA}
      {Research Assistant}{May-July 2016}
      \resumeItemListStart
        \resumeItem{Bench Marks}
          {Implemented and modified OpenCL benchmarks for floating point research}
        \resumeItem{Analysis}
          {Ran benchmarks on different hardware platforms, collected and analyzed results}
      \resumeItemListEnd

    \resumeSubheading
      {Basis Science, Intel}{San Francisco CA}
      {Engineer Coop}{July-Dec 2015}
      \resumeItemListStart
        \resumeItem{Drivers}
          {Sensor and flash memory drivers in embedded C}
        \resumeItem{Tools}
          {Test and data generation for learning algorithms}
      \resumeItemListEnd

    \resumeSubheading
      {EMC}{Franklin MA}
      {Engineer Coop}{July-Dec 2014}
      %\resumeItemListStart
      %\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumePub{Z. Wang, B. Crafton, T. Tomas-Gomez, X. Ruijuan, A. Luo, Z. Krivokapic, L. Martin, S. Datta, A. Raychowdhury, and A. Khan. Experimental demonstration of ferroelectric spiking neurons for unsupervised clustering. In ElectronDevices Meeting (IEDM), 2018 IEEE International. IEEE, 2018}
    \resumePub{Bayati, Mahsa, Brian Crafton, Miriam Leeser, Yijia Gu, and Thomas Wahl. Identifying Volatile Numeric Expressions in OpenCL Applications.}
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Compiler - Assembler - Processor}
      {Out of order, superscalar processor with branch prediction in Verilog. Compiler, assembler, test bench, and emulator.}
    \resumeSubItem{Memory Simulator}
      {DRAM and cache memory simulator for the processor project}
    \resumeSubItem{Parallel Neural Network}
      {Parallel programming project. Written in C, MPI, OpenMP.}
    \resumeSubItem{Wireless Speakers}
      {Lead of senior capstone design. Synchronized wireless speakers.}
    \resumeSubItem{Data Structures}
      {C implementation of 15 popular data structures}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
    {C, C++, Python}
    \resumeSubItem{HDL}
    {Verilog, System Verilog}
    \resumeSubItem{Technologies}
    {Debugger, Oscilloscope, Git, Perforce, Simulation, Synthesis, Place and Route tools}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
\grid
\grid
